\documentclass[a4paper, 12pt]{report}

\begin{document}

\title{Constitution}
\author{UK Community of Research Software Engineers}

\maketitle


% I've pretty much copied this from http://www.communityactionmk.org/support-and-information-for-groups/setting-up-and-running-a-group/simple-constitution-template/
% feel free to change.

\section{Name}

The name of the organisation shall be The UK Community of Research Software Engineers

\section{Mission Statement}

1 sentence summary of what we do

\section{Aims}

The organisation aims to:

\begin{itemize}
\item{Encourage academic institutions to appreciate the need for and fund RSE roles}
\item{Gain recognition for RSE outputs for staff on an academic track from grant awarding bodies, academic promotion committees, Research Excellence Framework }
\item{Provide support, training and networking opportunities for our members}
\end{itemize}

\section{Powers}

In order to achieve its aims, the group may:

\begin{itemize}
\item{Raise money}
\item{Open bank accounts}
\item{Take out insurance}
\item{Organise courses and events}
\item{Work with similar groups and exchange information and advice with them}
\item{Do anything that is lawful which will help to fulfil its aim}
\end{itemize}

\section{Membership}

Membership of the Group shall be open to any individual over eighteen without regards to disability, political or religious affiliation, race, sex or sexual orientation who is:\\

\begin{itemize}
\item{interested in helping the Group to achieve its aim}
\item{willing to abide by the rules of the Group}
\item{willing to pay any subscription agreed by the Management Committee}
\end{itemize}

The membership of any member may be terminated for good reason by the Management Committee: Provided that the member concerned shall have the right to be heard by the Management Committee, accompanied by a friend, before a final decision is made.\\

\section{Management Committee}

The Group shall be administered by a Management Committee of not less than three and not more than [insert number] individuals elected at the Group?s Annual General Meeting (A.G.M.).

The Officers of the Management Committee shall be: the Chairperson, the Treasurer and the Secretary.

The Management Committee may co-opt onto the Committee, up to three individuals, in an advisory and non-voting capacity that it feels will help to fulfil the aim of the Group.

The Management Committee shall meet at least two times a year. [check if this is feasible for your group - you can meet more often]

At least three Management Committee members must be present for a Management Committee meeting to take place.

Voting at Management Committee meetings shall be by a show of hands. If there is a tied vote then the Chairperson shall have a second vote.

The Management Committee shall have the power to remove any member of the Committee for good and proper reason.

The Management Committee may appoint any other member of the Group as a Committee member to fill a vacancy, provided that the maximum prescribed is not exceeded.


\section{Duties of the Committee Members}

\section{Finance}

All monies received by or on behalf of the Group shall be applied to further the aim of the Group and for no other purpose.

Any bank accounts opened for the Group shall be in the name of the Group.

Any cheques issued shall be signed by the Treasurer and one other nominated member of the Management Committee.

The Group shall ensure that its accounts are audited or independently examined every year.

The Group may pay reasonable out of pocket expenses including travel, childcare and meal costs to members or Management Committee members.




\section{Annual General Meeting}

The Group shall hold an Annual General Meeting (A.G.M.) in the month of [insert month]

All members shall be given at least fourteen days notice of the A.G.M. and shall be entitled to attend and vote.

The business of the A.G.M. shall include:

\begin{itemize}
\item{receiving a report from the Chairperson on the Group?s activities over the year}
\item{receiving a report from the Treasurer on the finances of the Group}
\item{electing a new Management Committee}
\item{considering any other matter as may be decided}
\end{itemize}

At least [insert number or percentage] members must be present for the Annual General Meeting and any other General Meeting to take place



\section{Special General Meeting}

A Special General Meeting may be called by the Management Committee or [insert number or percentage] members to discuss an urgent matter. The Secretary shall give all members fourteen days notice of any Special General Meeting together with notice of the business to be discussed.

 
\section{Alterations to the Constitution}

Any changes to this Constitution must be agreed by at least two-thirds of those members present and voting at any General Meeting.



\section{Dissolution}

The Group may be wound up at any time if agreed by two-thirds of those members present and voting at any General Meeting. In the event of winding up any assets remaining after all debts have been paid shall be given to another Group with a similar aim.



\section{Adoption of the Constitution}

Until the first A.G.M. takes place the persons whose names, addresses and signatures appear at the bottom of this document shall act as the Management Committee referred to in this constitution.


This Constitution was adopted on by


Name

Address


Signed



\end{document}